%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% can use \iftrue {block} \fi to pick and choose which details you want

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% For link formatting
\usepackage{fancyhdr,graphicx,xcolor,colortbl}
\usepackage{hyperref}


% Set applicant's personal data for header
\name{Ryan Elliott}
\address{6736 Ridge Road \linebreak Marriottsville MD 21104}
\contacts{443-340-0737 \linebreak rce3986@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
  % Change depending on the job
  \begin{cvsection}{Objective}
    
    \begin{cvsubsection}{}{}{}
      \iftrue
      I am a student at the University of Maryland, College Park in my Senior year. I am seeking a position as a Software Engineer %
      \fi
      \iffalse
      at AT\&T %
      \fi
      \iftrue
      to further my skills in back end development and gain experience working with skilled developers.
      \fi
    \end{cvsubsection}
    
  \end{cvsection}

  \begin{cvsection}{Employment}
    \begin{cvsubsection}{Sunnyvale, CA}{Walmart}{Summer 2022}
      \begin{center}
        \begin{itemize*}
          \item Software Engineering Intern
          \item Walmart \texttt{+}
          \item Back End
          \item ~
        \end{itemize*}
      \end{center}
      \begin{itemize}
        \item Orchestration level proof of concept project using Java, Spring, Maven, and GraphQL.
        \item Wrote project in Intellij and tested using Postman and Walmart's development web environment.
        \item Agile process flow with two week sprints; JIRA for development planning and Confluence for documentation.
        \item Receive HTTP request, authenticate request, call core API to retrieve necessary data, transform data for FE, %
        and return fields specified by GraphQL query.
        \item Used RestController annotated class for capturing HTTP request, Service annotated class for loading resources %
        and building GraphQL wiring, and DataFetcher class for retrieving and transforming data from core.
      \end{itemize}
    \end{cvsubsection} 
  \end{cvsection}

  \begin{cvsection}{Languages, Technologies, Frameworks, and Environments}
    \begin{cvsubsection}{}{}{}	
      \begin{itemize*}
        \item Python
        \item Java
        \item OCaml
        \item C
        \item Swift
        \item Verilog
        \item CAD
        \item Inventor
        \item GraphQL
        \item Spring
        \item Maven
        \item Eclipse
        \item Xcode
        \item Intellij
        \item Vivado
        \item VSCode
        \item Postman
        \item Laravel
        \item PHP
      \end{itemize*}
    \end{cvsubsection}
  \end{cvsection}

  \begin{cvsection}{Projects}
    \begin{cvsubsection}{Team}{Activate}{Fall 2022}
      \begin{itemize}
        \item Tasked with providing a means for teachers to track attendance and participation in classes.
        \item Built a web application with PHP Laravel framework on a Debian server.
        \item Gained experience setting up Laravel and building a back end for a web application.
        \item Gained experience with process, planning, and team coordination.
      \end{itemize}
    \end{cvsubsection}
    \begin{cvsubsection}{Individual}{MyTrips}{Winter 2021}
      \begin{itemize}
        \item iOS app made entirely with Swift in Xcode.
        \item This app can calculate a route given a start and end location and store that route on an iOS device.
        \item Once routes are stored, they can be viewed, deleted, or exported as a .csv file.
        \item Gained experience building basic iOS apps with both storyboards and programmatic front end.
      \end{itemize}
    \end{cvsubsection}
    \iffalse
    \begin{cvsubsection}{Team}{OSV}{Fall 2019}
      \begin{itemize}
        \item Engineering design project consisting of a team of six tasked with designing an OSV (over sand vehicle) to %
        complete an obstacle course. 
        \item Designed, built, tested, and presented our solution. 
        \item I took a leadership role in the group and got very positive feedback from teammates for my contributions.
      \end{itemize}
    \end{cvsubsection}
    \fi
    \iffalse
    \begin{cvsubsection}{Team}{CCCTC Senior Project}{Fall 2018}
      \begin{itemize}
        \item Engineering design project consisting of a team of three tasked with identifying a problem, designing a solution,%
        building a product, and showcasing it.
        \item Gained experience working in a team of engineers on a semester long project.
      \end{itemize}
    \end{cvsubsection}
    \fi
  \end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{College Park, MD}{University of Maryland}{Fall 2019 -- Spring 2023}
      \begin{center}
        \begin{itemize*}
          \item B.S. in Computer Engineering
          \item GPA: 3.734
          \item Academic Honors
          \item ~
        \end{itemize*}
      \end{center}
			\begin{itemize}
        \item Year 4: Computational Methods, Foundations of Machine Learning
        \item Year 3: Advanced Data Structures, Computer Organization and Design, Linear Algebra, Probability and Statistics, %
        Circuits, Systems and Signal Theory, Verilog
        \item Year 2: C, Assembly, Discrete Math, Algorithms, OCaml, Digital Logic Design, Signal Analysis
        \item Year 1: Object Oriented Java, Data Structures
			\end{itemize}
		\end{cvsubsection}
    \begin{cvsubsection}{Westminster, MD}{CC Career and Tech Center}{Fall 2017 / Fall 2018}
      \begin{center}
        \begin{itemize*}
          \item Project Lead the Way - Engineering
          \item ~
        \end{itemize*}
      \end{center}
			\begin{itemize}
        \item Year 2: Digital Electronics, CNC Milling, Robotics
        \item Year 1: CAD, Workshop Machinery, Design
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

  \begin{cvsection}{Links}
    \begin{cvsubsection}{}{}{}	
      \begin{itemize*}
        \item {\color{blue}\underline{\href{https://terpconnect.umd.edu/~ryane3/}{Personal Website}}}
        \item {\color{blue}\underline{\href{https://www.linkedin.com/in/ryan-elliott-04a31721b/}{LinkedIn}}}
        \item {\color{blue}\underline{\href{https://github.com/rce3986}{GitHub}}}
      \end{itemize*}
    \end{cvsubsection}
  \end{cvsection}

\end{document}